Analyzing Security-Cost Trade-off for a \\ Fully Homomorphic Encryption Scheme

### 2013-06-18 Report/article.tex
gg

\subsection{Cost of the Cryptosystem}
 In the SV scheme, performing any operation on encrypted bits requires  \texttt{KeyGen}, \texttt{Encrypt}, \texttt{Add},\texttt{ Mult}, \texttt{Recrypt}, \texttt{Decrypt}, and hence we measure their performance in terms of run time. These measurements are done by varying the parameter $N$(keeping all other parameters fixed) that determines the degree of all intermediate polynomials of the cryptosystem. The measurements in this section were taken on M2. From \autoref{common cost}, we can infer that the cost of these functions increase with the increase of the degree of the polynomial $F(x)$. Futhermore, we observe that the size of the public key is increasing with the increase of $N$ which can be explained by the fact that the resultant of 2 polynomials increases with the increase of the degree which makes the prime number $p$ harder to be found and so it increases the duration of key generation.

>>>>

\subsection{Cost of the Cryptosystem}
 In the SV scheme, performing any operation on encrypted bits requires  \texttt{KeyGen}, \texttt{Encrypt}, \texttt{Add},\texttt{ Mult}, \texttt{Recrypt}, \texttt{Decrypt}, and hence we measure their performance in terms of run time. These measurements are done by varying the parameter $N$(keeping all other parameters fixed) that determines the degree of all intermediate polynomials of the cryptosystem. The measurements in this section were taken on M2. From \autoref{common cost}, we can infer that the cost of these functions increase with the increase of the degree of the polynomial $F(x)$. Futhermore, we observe that the size of the public key is increasing with the increase of $N$ which can be explained by the fact that the resultant of 2 polynomials increases with the increase of the degree which makes the prime number $p$ harder to be found and so it increases the duration of key generation. The same thing for encrypt which evaluate a polynomial of degree $N$ so it take more time for bigger $N$ and it generates bigger ciphertexts. The decryption function also increases in duration because $p$ and the cpiphertext become bigger with increasing $N$. And for the other functions, the increase in duration is explained by the increase of the size of ciphertexts which makes the addition and multiplication more difficult.
